---
title: "HW_1"
author: "nr2774"
date: 2022-09-22
output: github_document
---

# Problem_1 ####

```{r problem_1}
data("penguins", package = "palmerpenguins")
penguins

nrow(penguins)

ncol(penguins)

df = penguins

mean (df$flipper_length_mm, na.rm = TRUE)

```

- Data in this dataset is about penguins which are Adeilie types and are from island called Torgersen. 
Valeues are included bill length, bill depth, flipper length and body mass , sex, and year. 

- The number of rows are 344
  The number of colums are 8 
  The mean flipper length is 200.9152

```{r problem_1_1}
library(tidyverse)
scatterplot = ggplot(penguins, aes(x = bill_length_mm,
                                   y = flipper_length_mm, 
                                   col = species)) + geom_point()

scatterplot

ggsave("HW1scatterplot.pdf", plot = scatterplot )
```


```{r problem_2}
library(tidyverse)

Data_frame = tibble(
  vec_norm = rnorm(10),
  vec_logical = vec_norm>0,
  vec_char = c("a", "b", "c", "a", "b", "c", "a", "b", "c", "d"),
  vec_factor = factor(c("low", "medium", "high", "low", "medium", "high",
                        "low", "medium", "high", "low"), levels= c( "low", "medium", "high"))

)

mean (Data_frame$vec_norm, na.rm = TRUE)
mean (Data_frame$vec_logical, na.rm = TRUE)
mean (Data_frame$vec_char, na.rm = TRUE)
mean (Data_frame$factor, na.rm = TRUE)

  
```

**Take the mean of vec for logical indicates that proprtion of people 
who got the treatment 


The purpose of this file is to present a couple of basic plots using `ggplot`.

First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
    ```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
