---
title: "HW_1"
author: "nr2774"
date: 2022-09-22
output: github_document
---

# Problem_1 ####

```{r}
data("penguins", package = "palmerpenguins")
penguins

nrow(penguins)

ncol(penguins)




```

- ?? the data in this dataset, including names / values of important variables

- Data in this dataset is about penguins which are Adeilie types and are from island called Torgersen. 
Valeues are included bill length, bill depth, flipper length and body mass , sex, and year. 

- The number of rows are 344
  The number of colums are 8 






```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to present a couple of basic plots using `ggplot`.

First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
