---
title: "HW_1"
author: "nr2774"
date: 2022-09-22
output: github_document
---

# Problem_1 


```{r}
#Loading in relevant packages. 
library(tidyverse)
```


```{r problem_1}
# Discription of the dataset 

data("penguins", package = "palmerpenguins")
penguins

nrow(penguins)

ncol(penguins)

mean(pull(penguins,flipper_length_mm), na.rm = TRUE)

```

Data in this dataset is about penguins. There are three type of penquins Adeilie,Chinstrap and Gentoo.These are from an island called Torgersen. 

Values are included as bill length, bill depth, flipper length and body
mass , sex, and year. 

The number of rows are 344 `
The number of colums are 8 
The mean flipper length is 200.9152

```{r scatterplot}
library(tidyverse)
scatterplot = ggplot(penguins, aes(x = bill_length_mm,
                                   y = flipper_length_mm, 
                                   col = species)) + geom_point()

scatterplot

ggsave("HW1scatterplot.pdf", plot = scatterplot )
```

Adelie (species) was indicated as Red dots.
Chinstrap (species) was indicated as green dots. 
Gentoo (species) was indicated as blue dots. 
The graphic shows the clustering of these species at particular space on the plot. 

ggsave comment was to save to scatterplot on PDF from on our file. 

# Problem_2

```{r problem_2}

Data_frame = tibble(
  vec_norm = rnorm(10),
  vec_logical = vec_norm>0,
  vec_char = c("a", "b", "c", "a", "b", "c", "a", "b", "c", "d"),
  vec_factor = factor(c("low", "medium", "high", "low", "medium", "high",
                        "low", "medium", "high", "low"), levels= c( "low", "medium", "high"))
)

Data_frame 
```

Data frame was created using tibble function. 


```{r}

mean(pull(Data_frame, vec_norm))
mean(pull(Data_frame, vec_logical))
mean(pull(Data_frame, vec_char))
mean(pull(Data_frame, vec_factor))
     
```



```{r}

as.numeric(pull(Data_frame, vec_norm))
as.numeric(pull(Data_frame, vec_logical))
as.numeric(pull(Data_frame, vec_char))
as.numeric(pull(Data_frame, vec_factor))

```

After using `as.numeric(pull(Data_frame, vec_logical))` for logical vector it lists the o and 1. When i apply logical factor R supplies value 0 is signed to false and 1 to true. I allows us to interpret these values as proportions. For instance, mean for logical was 0.2 that means 2 of the values were true

Appying `as. numeric` command for logical, character and factor variables, it converts charater values to numeric . So that now R knows that mean can be calculated were was it was not possible in the previous mean command. Not the nean of `as.numeric(pull(Data_frame, vec_factor))` can be calculated where as it was not possible with previous just mean command.  

