---
title: "HW_1"
author: "nr2774"
date: 2022-09-22
output: github_document
---

# Problem_1 ####

```{r problem_1}
data("penguins", package = "palmerpenguins")
penguins

nrow(penguins)

ncol(penguins)

df = penguins

mean (df$flipper_length_mm, na.rm = TRUE)

```

- Data in this dataset is about penguins which are Adeilie types and are from island called Torgersen. 
Valeues are included bill length, bill depth, flipper length and body mass , sex, and year. 

- The number of rows are 344
  The number of colums are 8 
  The mean flipper length is 200.9152

```{r problem_1_1}
library(tidyverse)
scatterplot = ggplot(penguins, aes(x = bill_length_mm,
                                   y = flipper_length_mm, 
                                   col = species)) + geom_point()

scatterplot

ggsave("HW1scatterplot.pdf", plot = scatterplot )
```


```{r problem_2}
library(tidyverse)

Data_frame = tibble(
  vec_norm = rnorm(10),
  vec_logical = vec_norm>0,
  vec_char = c("a", "b", "c", "a", "b", "c", "a", "b", "c", "d"),
  vec_factor = factor(c("low", "medium", "high", "low", "medium", "high",
                        "low", "medium", "high", "low"), levels= c( "low", "medium", "high"))

)
  
```

```{r}

mean(pull(Data_frame, vec_norm))
mean(pull(Data_frame, vec_logical))
mean(pull(Data_frame, vec_char))
mean(pull(Data_frame, vec_factor))
     
```



```{r}

as.numeric(pull(Data_frame, vec_norm))
as.numeric(pull(Data_frame, vec_logical))
as.numeric(pull(Data_frame, vec_char))
as.numeric(pull(Data_frame, vec_factor))

```

After using `as.numeric(pull(Data_frame, vec_logical))` for logical vector it lists the 

When i supply logical factor R supplies value 0 is signed to false and value 1 is signed to true. I allows us to interpret these values as proportions. For instance, mean for logical was 0.2 that means 2 of the values were true.




Some  freaction of population was given the 



For apppying as. numeric command for logical, character and factor variables, this convering charater an

